---
title: "p8105_hw6_cl4044"
author: "Chenxi Liu"
date: "12/7/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(p8105.datasets)
```

### Problem 1

```{r}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```



## Problem 2

Import and tidy the dataset 
```{r}
baby_df = 
  read_csv("./data/birthweight.csv") %>%
  janitor::clean_names() %>%
  mutate(
    across(
      .cols = c("frace", "mrace"),
      ~ case_when(
        .x == 1 ~ "White",
        .x == 2 ~ "Black",
        .x == 3 ~ "Asian",
        .x == 4 ~ "Puero Rican",
        .x == 8 ~ "Other",
        .x == 9 ~ "Unknown"
        )
    ),
    across(where(is.character), as.factor)
    ) %>%
  mutate(
    babysex = case_when(
      babysex == 1 ~ "male",
      babysex == 2 ~ "female"
      ), 
     malform = case_when(malform == 0~"absent", 
                         malform == 1 ~ "present"),
    across(where(is.character), as.factor)
  )
      
      
```

Stepwise regression model
```{r}
full_model = lm(bwt ~ ., data = baby_df) 
step_model <- MASS::stepAIC(full_model, direction = "both", 
                      trace = FALSE)
step_model %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


Plot predicton values vs. residuals

```{r}
baby_df %>% 
  modelr::add_residuals(step_model) %>% 
  modelr::add_predictions(step_model) %>%
  ggplot(aes(x = pred, y = resid)) + 
  geom_point(alpha = 0.3) +
  labs(
    title = "Predicton vs. Residual",
    x = "Predicton",
    y = "Residual"
  )
```

According to the plot above, most of the points are clustered around zero. There are some large residual points when prediction value is under 1000. 

Model 2: One using length at birth and gestational age as predictors (main effects only)
```{r}
model_2 = lm(bwt ~ blength + gaweeks, data = baby_df) %>%
  broom::tidy() %>% 
  knitr::kable(digits = 3)
model_2
  
```

Model 3: One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
model_3 = lm(bwt ~ bhead * blength * babysex, data = baby_df) %>%
  broom::tidy() %>% 
  knitr::kable(digits = 3)
model_3
```



## Problem 3

Import the dataset 
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```

